\thispagestyle{empty}
\begin{center}
    \Large \bfseries  {ACKNOWLEDGEMENT} \\[1cm] 
\end{center}

\vspace{2\baselineskip}

\noindent
\par
I am grateful for the support and guidance I received from many people, which made this project successful. I would like to thank my supervisor, Dr. Ajees A P, Assistant Professor in the Department of Computer Science at CUSAT. His constant motivation, insightful suggestions, and unwavering support were crucial for the completion of this project. \par

 I would also like to thank Dr. Madhu S. Nair, the Head of the Department of Computer Science, for providing me with exuberant facilities. 
 
 \par I am thankful to Dr. Shailesh S., Assistant Professor in the Department of Computer Science, for his valuable practicals and trainings in addition to his regular teaching sessions.
 
 \par I appreciate Dr. Jeena Kleenankandy, Assistant Professor in the Department of Computer Science, for teaching me NLP concepts and proving more thoughtful insights about various concepts. 
 
 \par I express my gratitude to all the faculty members and non-teaching staff in the Computer Science department for their marvelous support during the project's execution. I am thankful to Cochin University of Science and Technology for allowing me to pursue this course. 
 
 \par I am also grateful for the encouragement and assistance I received from my parents, spouse, friends, and colleagues, who supported me through the busiest times during the project. Lastly, I thank the Almighty for giving me the courage, knowledge, wisdom, and ability to undertake this work.

\vspace{1\baselineskip}
\noindent
\myname 

