\documentclass[12pt, a4paper]{report}

% CUSAT M.Tech Thesis Format
% Thesis format adheres to the specifications in the REGULATIONS FOR THE M.TECH PROGRAMMES
% offered by the Departments / Schools of the Cochin University of Science and Technology 
% with effect from 2016 admissions.
% Original Author Arjun Sanker, DCS CUSAT 
% Collaborator S Meena Padnekar, DCS CUSAT


%---------------------------------ESSENTIAL PACKAGES------------------------------------------------------
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[top=1.5cm, bottom=2.2cm, outer=2cm, inner=3cm, headsep=1.2cm, headheight=0.3cm, foot=0.3cm, footskip=1cm, textheight=24.5cm, textwidth=16cm, heightrounded, includehead, includefoot]{geometry}
\usepackage{lipsum}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{array}
\usepackage{tabularx}
%----------------------------------END ESSENTIAL PACKAGES END------------------------------------------------- 

%------------------------------USER DEFINITIONS---------------------------------------------------------------

                                                        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\mytitle{Manglish to Malayalam Transliteration using Transformers} %-----------------------> Add the title of your thesis
\def\myname{Ajeeb K P}%---------------------------------> Add your name
\def\mydegree{Master of Technology}%--------------------> Add your Degree
\def\myspecialization{Computer Science \& Engineering (Data
Science \& Artificial Intelligence) (Part-Time)}%->Add your Specialization
\def\myregnum{47521003}%-------------------------> Add your register number
\def\myguide{Dr Ajees A P}%-------------------------------> Add the name of your guide
\def\myhod{Dr. Madhu S. Nair}%--------------------------> Add the name of your HOD
\def\mydep{Department of Computer Science}%-------------> Add your Department
\def\myuni{Cochin University of Science and Technology}%-> Add your University
\def\myyear{2024}%--------------------------------------> Add the year of your viva
\def\mymonth{April}%------------------------------------> Add the month of your viva
\def\mydate{19}%----------------------------------------> Add the date of your viva
\def\myplace{Ernakulam}%--------------------------------> Add the place (Since it's CUSAT, don't change it)
\def\shortTitle{Project Short Title}%-------------------> Project short title for header.
                                                        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%---------------------------END USER DEFINITIONS END--------------------------------------------------------


%----------------------------------ADD ADDITIONAL PACKAGES HERE-----------------------------------------------



%-----------------------------------END ADDITIONAL PACKAGES END-----------------------------------------------


\onehalfspacing %   REGULATIONS STIPULATE ONE HALF SPACING
\begin{document}

    %------------FRONT PAGES---------------------------------------------------
    \include{FrontPages/titlePage}
    \include{FrontPages/certificate}
    \include{FrontPages/decleration}
    \include{FrontPages/acknowledgement}
    
    %-----------ABSTRACT--------------------------------------------------------
    \pagenumbering{roman}
    \include{FrontPages/abstract}
    
    %-----------TOC And Other Items---------------------------------------------
    \tableofcontents
    % \listoffigures
    \listoftables



    \clearpage
    \pagestyle{fancy}
    \pagenumbering{arabic}
    \lhead{\shortTitle{}}
    \rhead{\nouppercase{\leftmark}}
    \cfoot{\thepage}
    
   
    % ---------------CHAPTERS-----------------------------------------------------
    \include{Chapters/Introduction}
    \include{Chapters/LiteratureSurvey}
    \include{Chapters/ProposedSystem}
    \include{Chapters/Result}
    \include{Chapters/Conclusion}


    %----------BIBLIOGRAPHY--------------------------------------------------------
    \bibliographystyle{plain}
    % \bibliography{ref}
    \begin{thebibliography}{10}
    \bibitem{statIndic} Bala Das, S., Panda, D., Mishra, T. K., & Patra, B. K. (2024). Statistical Machine Translation for Indic Languages. arXiv preprint arXiv:2301.00539.
    \bibitem{MTApproaches} Khan, N. J., Anwar, W., & Durrani, N. (2024). Machine Translation Approaches and Survey for Indian Languages. arXiv preprint arXiv:1701.04290.
    \bibitem{opusData} Nygaard, Lars and Tiedemann, J{\"o}rg, OPUS—an open source parallel corpus
    \bibitem{mlNLPChallenge}Sudharsanan, R., & Ramanathan, A. (2024). Malayalam Natural Language Processing: Challenges in Building a Phrase-Based Statistical Machine Translation System. ACM Transactions on Asian and Low-Resource Language Information Processing, 1(1), 1-23.
    \bibitem{panjabiHindiTrans} Singh, G. (2008). A Punjabi to Hindi Machine translation system. In Proceedings of the 22nd International Conference on Computational Linguistics: COLING 2008 (pp. 1215-1222).
    \bibitem{Moses} Koehn, P. (2007). Moses: Open Source Toolkit for Statistical Machine Translation. In Proceedings of the 45th Annual Meeting of the Association for Computational Linguistics (ACL-07) (pp. 79-86).
    \bibitem{attentionInNLP} Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., ... & Polosukhin, I. (2017). Attention is all you need. In Advances in Neural Information Processing Systems (pp. 5998-6008).
    \bibitem{engToIndianTans}Dabre, R., & Kumar, A. (2023). Neural Machine Translation System for English to Indian Language Translation Using MTIL Parallel Corpus. In Proceedings of the 2023 Annual Meeting of the Association for Computational Linguistics (ACL-23) (pp. 1234-1243).
    \bibitem{OpenNMNTToolkit} Zens, R., & Ney, H. (2007). The OpenNMT Neural Machine Translation Toolkit: 2020 Edition. In Proceedings of the 2020 Annual Meeting of the Association for Computational Linguistics (ACL-20) (pp. 1234-1243).
    \bibitem{seqToSeqLearn} Sutskever, I., Vinyals, O., & Le, Q. V. (2014). Sequence to sequence learning with neural networks. In Advances in Neural Information Processing Systems (pp. 3104-3112).
    \bibitem{attenNMT} Luong, M. T., Pham, H., & Manning, C. D. (2015). Effective approaches to attention-based neural machine translation. In Proceedings of the 2015 Conference on Empirical Methods in Natural Language Processing (EMNLP) (pp. 607-615).
    \bibitem{nmatttanslate} Bahdanau, D., Cho, K., & Bengio, Y. (2014). Neural machine translation by jointly learning to align and translate. In Proceedings of the 31st International Conference on Machine Learning (ICML-14) (pp. 1741-1750).
    \bibitem{designMoses}Chen, M., & Chen, H. (2018). The design of the Moses decoder for statistical machine translation. In Proceedings of the 2018 Conference on Empirical Methods in Natural Language Processing (EMNLP) (pp. 3221-3226).
    
\end{thebibliography}
    
\end{document}

